Reduced plasticity and opportunity for selection in terrestrial ectotherm populations under climate change

### 2023-05-25 ms.qmd
Delete some code

  # We can summarise this across the habitat types
    all_pred2_no_sum2  %>% group_by(habitat) %>% summarise(mean = mean(est_per, na.rm = TRUE), 
                                                            l95 = mean(est_perl95, na.rm = TRUE), 
                                                            u95 = mean(est_peru95, na.rm = TRUE))

# Need to take a step back
  # 1. Why do we have NA in this data set? Thats because some species in the Future projections don't have data!
  # 2. Why are l95 and u95 for marine not working...no idea
  # 3. Apply to the posteriors, rather than summary. Working on this....

>>>>

# Need to take a step back
  # 1. Why do we have NA in this data set? Thats because some species in the Future projections don't have data!
  # 2. Why are l95 and u95 for marine not working...Fixed
  # 3. Apply to the posteriors, rather than summary. Done
